\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-27 tex/ms.tex
done for the day

@@

% \begin{figure}[t!]
%     \begin{centering}
%     \includegraphics[width=\linewidth]{figures/map_labels.pdf}
%     \caption{\label{fig:map_labels}
%             Map of Sol d with the major features indicated with suggested
%             names.
%             \codelink{earthshine_S1_S2}
%             }
%     \end{centering}
% \end{figure}

@@

\todo{Residuals in Figure~\ref{fig:model} display significant correlated
structure. Talk about their power spectrum. Temporal fit helps. Discuss
Figure~\ref{fig:map_temporal} and argue we have evidence for clouds.}

@@

\subsection{Application to Other Planets}
\label{sec:otherplanets}

\todo{Discuss how we would we do this for an actual exoplanet, and
all the homework we need to do before that happens.}

@@

\todo{(summarize)}

\todo{(utility for \TESS background removal)}

\todo{(talk abt prospects for doing this analysis with exoplanets)}

>>>>

\todo{We need to cite} \citep{Berdyugina2017,Cowan2009,Cowan2018,Haggard2018,Kawahara2010,Fujii2012,Lustig-Yaeger2018} and others.

\todo{We need to cite}\citep{Knutson2007,Majeau2012,deWit2012} on the first maps of an exoplanet.

@@

@@

As we mentioned in \S\ref{sec:results}, the residuals about our maximum
likelihood fit show correlated structure with power at a large range
of periods ranging from 0.1 up to 10 days. This is likely due to 
the fact that rotational variability is not the sole source of the
signal of Sol d: additionally, there is likely temporal variation in the 
albedo of certain parts of the map, most probably due to cloud movement.
In order to test this, we used \starry to construct a time-variable
spherical harmonic map, defined by a vector of spherical harmonic coefficients
that varies slowly over time:
%
\begin{align}
    \mathbf{y}(t) = \sum_{n=0}^N \mathbf{y}_n c_n(t)
\end{align}
%
where the $\mathbf{y}_n$ are the $N$ spherical harmonic coefficient
vectors that describe the temporal variability and the $c_n$ are the components
of the basis in time. Since this is a linear operation on the spherical
harmonic coefficients, the \starry model is still linear, and may be
solved in the same way as before.

We choose the $c_n$ vectors to be an orthogonal polynomial basis in time of 
degree 6 spanning all of Sector 1. Under this basis, one can 
approximately interpret
$\mathbf{y}_0$ as the static component of the map, $\mathbf{y}_1$ as the
component that varies quasi-linearly in time, $\mathbf{y}_2$ as the component
that varies quasi-quadratically, and so forth. In all, we fit for six
of these map components.

We neglect the data taken in Sector 2, focusing instead on the portion of the data for which
we have good temporal coverage. In order to mitigate overfitting due to
the larger number of variables we are solving for,
we add a term to our likelihood function that forces the coefficients
of the $n > 0$ maps to remain small. We further evaluate the albedo of the map
on a grid at six equally spaced points in time, enforcing our albedo and
power spectrum priors separately at each of these points.

@@

The mean of the temporal solution is shown in Figure~\ref{fig:map_temporal},
and a link to an animated version is provided in the caption. No significant
differences are evident, although the residuals improved by ${\sim}30\%$
and contain significantly less power on timescales longer than 1 day.
We conclude that while this is evidence for cloud variability on these
timescales, a more detailed investigation is warranted to say anything
meaningful about the dynamics of clouds on Sol d.

\subsection{Implication for Future Observations}
\label{sec:otherplanets}

Observed in the \tess band, Sol d is a planet dominated by
clouds. \todo{Discuss how this problem is *hard* and how we need
large time baseline to disentangle clouds from continents, and even
then there are cloud features that are stationary, so hard to
tell apart. What we really need is multi-band photometry,
as suggested in \cite{Cowan2009}.}

@@

\todo{(summarize)}
\todo{(talk abt prospects for doing this analysis with exoplanets)}
